---
title: "Workflow 00 search scoping report"
output:
  html_document:
    toc: false
    self_contained: true
params:
  counts_csv: "outputs/workflow00_search_scope/search_scope_counts.csv"
  counts_json: "outputs/workflow00_search_scope/search_scope_counts.json"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(jsonlite)

counts <- read.csv(params$counts_csv, stringsAsFactors = FALSE, na.strings = "")
meta <- fromJSON(params$counts_json, simplifyVector = FALSE)

fmt_hits <- function(x) {
  ifelse(is.na(x), "", format(as.integer(x), big.mark = ",", scientific = FALSE))
}
counts$Hits <- fmt_hits(counts$hits)
report_table <- counts[, c("source", "search_date", "Hits", "status")]
names(report_table) <- c("Search source", "Search date", "Hits", "Status")
```

This report records a **count-only scoping search** for the current Workflow 00 search strategy. No bibliographic search-result records or raw API responses were retained.

**Search version:** `r meta$search_version`  
**Scoping date:** `r meta$search_date`

## Search strategy

Species concept:

`r paste(meta$immutable_species_terms, collapse = " OR ")`

Farm/aquaculture concept:

`r paste(meta$base_farm_terms, collapse = " OR ")`

Source-specific field syntax was generated by the same Workflow 00 query planner used for production searching.

## Search counts

```{r counts}
knitr::kable(
  report_table,
  row.names = FALSE,
  align = c("l", "l", "r", "l"),
  caption = "Reported database hit counts at the time of the scoping search."
)
```

CAB Abstracts and ProQuest Dissertations & Theses Global are currently manual-ingest Workflow 00 sources and therefore do not have an automated API count in this report.
