---
title: "Workflow 00 search scoping report"
output:
  html_document:
    toc: false
    self_contained: true
params:
  counts_csv: "outputs/workflow00_search_scope/search_scope_counts.csv"
  counts_json: "outputs/workflow00_search_scope/search_scope_counts.json"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(jsonlite)

counts <- read.csv(params$counts_csv, stringsAsFactors = FALSE, na.strings = "")
meta <- fromJSON(params$counts_json, simplifyVector = FALSE)

fmt_hits <- function(x) {
  ifelse(is.na(x), "", format(as.integer(x), big.mark = ",", scientific = FALSE))
}
counts$Hits <- fmt_hits(counts$hits)
report_table <- counts[, c("source", "search_date", "Hits", "status")]
names(report_table) <- c("Search source", "Search date", "Hits", "Status")
```

This report records a **count-only scoping search**. No bibliographic search-result records or raw API responses were retained.

**Scoping date:** `r meta$search_date`  
**Search input:** `r meta$search_input_path`  
**Boolean validation:** PASS

## Search string

```
`r meta$original_search_string`
```

The search string was validated before any API request for balanced double quotes, balanced parentheses, valid Boolean grammar, and database-neutral syntax. Source-specific field syntax was then generated from this validated expression.

## Search counts

```{r counts}
knitr::kable(
  report_table,
  row.names = FALSE,
  align = c("l", "l", "r", "l"),
  caption = "Reported database hit counts at the time of the scoping search."
)
```

CAB Abstracts and ProQuest Dissertations & Theses Global are manual-ingest Workflow 00 sources. Their rows report the validated result totals recorded in the current W00 source registries rather than live API counts.
