---
title: "The status of academic research on salmon farming: a living evidence map"
subtitle: "Results"
output:
  word_document:
    toc: false
  html_document:
    toc: true
    toc_float: true
bibliography: references.bib
link-citations: true
reference-section-title: References
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(dplyr)
library(tidyr)
library(stringr)
library(readr)
library(jsonlite)
library(here)

source(here::here("visualisations", "canonical_figure_data.R"))

# -------------------------------------------------------------------------
# Authoritative analytical state
# -------------------------------------------------------------------------
# Every evidence-map number and topic name in the prose below is calculated
# at render time from the latest included-only canonical JSONL. Workflow-flow
# counts are produced by 07_flow_diagram.R from authoritative pipeline inputs
# in the same Workflow 09 run.

master <- load_figure_master()
n_total <- nrow(master)

fmt <- function(x) format(as.integer(x), big.mark = ",", scientific = FALSE, trim = TRUE)
pct <- function(x, denominator = n_total) sprintf("%.1f%%", 100 * as.numeric(x) / denominator)
human_list <- function(x) {
  x <- as.character(x)
  if (!length(x)) return("")
  if (length(x) == 1L) return(x)
  if (length(x) == 2L) return(paste(x, collapse = " and "))
  paste0(paste(x[-length(x)], collapse = ", "), ", and ", x[length(x)])
}

include_figure <- function(...) {
  candidates <- c(...)
  hit <- candidates[file.exists(candidates)]
  if (!length(hit)) stop("Missing manuscript figure: ", paste(candidates, collapse = " | "), call. = FALSE)
  knitr::include_graphics(hit[[1L]])
}

# -------------------------------------------------------------------------
# Publication year
# -------------------------------------------------------------------------

year_counts <- master %>%
  filter(!is.na(year)) %>%
  distinct(record_id, year) %>%
  count(year, name = "n")

current_year <- as.integer(format(Sys.Date(), "%Y"))
complete_years <- year_counts %>% filter(year < current_year)
latest_complete_year <- max(complete_years$year)
latest_complete_n <- complete_years$n[match(latest_complete_year, complete_years$year)]
year_n <- function(y) {
  out <- year_counts$n[match(y, year_counts$year)]
  ifelse(length(out) && !is.na(out), out, 0L)
}

# -------------------------------------------------------------------------
# Species
# -------------------------------------------------------------------------

species_counts <- master %>%
  transmute(record_id, species = final_species) %>%
  separate_rows(species, sep = ";") %>%
  mutate(species = str_trim(species)) %>%
  filter(!is.na(species), species != "") %>%
  distinct(record_id, species) %>%
  count(species, name = "n", sort = TRUE)

nth_species <- function(n) species_counts[n, , drop = FALSE]

# -------------------------------------------------------------------------
# Geography
# -------------------------------------------------------------------------

gazetteer <- read_csv(
  here::here("config", "global_country_gazetteer_v3.csv"),
  show_col_types = FALSE,
  progress = FALSE
)

country_lookup <- gazetteer %>%
  transmute(
    iso3c = toupper(str_trim(as.character(iso3c))),
    country_name = str_trim(as.character(country_name)),
    match_type = tolower(str_trim(as.character(match_type))),
    priority = suppressWarnings(as.numeric(priority))
  ) %>%
  filter(
    !is.na(iso3c), iso3c != "",
    !is.na(country_name), country_name != "",
    match_type %in% c("country", "country name")
  ) %>%
  arrange(iso3c, desc(priority), country_name) %>%
  distinct(iso3c, .keep_all = TRUE) %>%
  select(iso3c, country_name)

country_counts <- master %>%
  transmute(record_id, iso3c = toupper(str_trim(as.character(final_primary_country_iso3c)))) %>%
  filter(!is.na(iso3c), iso3c != "") %>%
  separate_rows(iso3c, sep = ";") %>%
  mutate(iso3c = toupper(str_trim(iso3c))) %>%
  filter(iso3c != "", iso3c != "NONE") %>%
  distinct(record_id, iso3c) %>%
  count(iso3c, name = "n", sort = TRUE) %>%
  left_join(country_lookup, by = "iso3c") %>%
  mutate(country_name = if_else(is.na(country_name) | country_name == "", iso3c, country_name))

nth_country <- function(n) country_counts[n, , drop = FALSE]

geo_status <- toupper(str_trim(as.character(master$geography_status)))
n_geo_coded <- sum(geo_status == "RESOLVED")
n_geo_uncoded <- sum(geo_status == "NONE")
stopifnot(n_geo_coded + n_geo_uncoded == n_total)

# -------------------------------------------------------------------------
# Topic hierarchy
# -------------------------------------------------------------------------

topic_records <- master %>%
  transmute(record_id, raw_paths = as.character(topic_hierarchy_paths)) %>%
  filter(!is.na(raw_paths), str_trim(raw_paths) != "") %>%
  mutate(path = str_split(raw_paths, "\\s*;\\s*")) %>%
  unnest(path) %>%
  mutate(
    path = str_squish(path),
    parts = str_split(path, "\\s*>\\s*"),
    level1 = vapply(parts, function(x) if (length(x) >= 1L) x[[1L]] else NA_character_, character(1)),
    level2 = vapply(parts, function(x) if (length(x) >= 2L) x[[2L]] else NA_character_, character(1)),
    level3 = vapply(parts, function(x) if (length(x) >= 3L) x[[3L]] else NA_character_, character(1))
  ) %>%
  filter(path != "") %>%
  distinct(record_id, path, .keep_all = TRUE)

topic_rank <- function(level = 1L, n = 1L, level1 = NULL, level2 = NULL, smallest = FALSE) {
  stopifnot(level %in% 1:3, n >= 1)
  d <- topic_records
  if (!is.null(level1)) d <- d %>% filter(.data$level1 == level1)
  if (!is.null(level2)) d <- d %>% filter(.data$level2 == level2)
  field <- paste0("level", level)
  out <- d %>%
    filter(!is.na(.data[[field]]), .data[[field]] != "") %>%
    distinct(record_id, name = .data[[field]]) %>%
    count(name, name = "n") %>%
    arrange(if (smallest) n else desc(n), name)
  if (n > nrow(out)) stop("Requested topic rank exceeds available topics.", call. = FALSE)
  out[n, , drop = FALSE]
}

topic_name <- function(level, n, level1 = NULL, level2 = NULL, smallest = FALSE) {
  topic_rank(level, n, level1, level2, smallest)$name[[1L]]
}
topic_count <- function(level, n, level1 = NULL, level2 = NULL, smallest = FALSE) {
  topic_rank(level, n, level1, level2, smallest)$n[[1L]]
}
topic_pct <- function(level, n, level1 = NULL, level2 = NULL, smallest = FALSE) {
  pct(topic_count(level, n, level1, level2, smallest))
}

n_topic_coded <- n_distinct(topic_records$record_id)
n_topic_uncoded <- n_total - n_topic_coded
n_topic_assignments <- nrow(topic_records)

# -------------------------------------------------------------------------
# Pipeline flow counts from the same Workflow 09 run
# -------------------------------------------------------------------------

flow_candidates <- c(
  Sys.getenv("FLOW_COUNTS_JSON", unset = ""),
  here::here("visualisations", "figure_07_flow_diagram_counts.json"),
  here::here("docs", "reporting", "workflow_09", "flow_counts.json")
)
flow_path <- flow_candidates[nzchar(flow_candidates) & file.exists(flow_candidates)][1]
if (is.na(flow_path) || !nzchar(flow_path)) stop("No Workflow 09 flow-count JSON available.", call. = FALSE)
flow <- fromJSON(flow_path, simplifyVector = FALSE)$counts

stopifnot(
  as.integer(flow$final_included) == n_total,
  n_topic_coded + n_topic_uncoded == n_total,
  n_geo_coded + n_geo_uncoded == n_total
)
```

# Results

## Review process

Following multi-database retrieval and reconciliation, `r fmt(flow$deduplicated_records)` deduplicated canonical records entered the curation pipeline. `r fmt(flow$retractions_excluded)` records were removed following the retraction/withdrawal sweep. Of the remaining `r fmt(flow$title_abstract_screened)` records, `r fmt(flow$title_abstract_excluded_total)` were excluded during title-and-abstract screening and subsequent eligibility quality control, leaving `r fmt(n_total)` records in the final included evidence map. The final canonical total independently reconciles with the Workflow 08 included-only JSONL used for all analyses below.

Database provenance was retained through deduplication, allowing the contribution and overlap of the five bibliographic sources to be compared before and after relevance screening. The paired UpSet-style figure shows database contribution to the deduplicated corpus and to the set retained at Workflow 04, together with the exact source intersections.

```{r fig-source-contribution, fig.cap="Contribution and overlap of bibliographic databases before and after relevance screening. Black bars show all deduplicated canonical records and blue bars show records retained at Workflow 04; the matrix identifies the database combination defining each exact intersection."}
include_figure(here::here("outputs", "citesource_contribution", "database_contribution_upset.png"))
```

The complete search, reconciliation, repair, screening and annotation process is summarised in the review flow diagram.

```{r fig-flow, fig.cap="Flow of records through database searching, deduplication, record repair and enrichment, retraction screening, title-and-abstract screening, annotation and inclusion in the Living Evidence Map."}
include_figure(here::here("visualisations", "figure_07_flow_diagram.png"))
```

## Publication year

The volume of academic evidence on salmon farming increased markedly over time. There were `r fmt(latest_complete_n)` included records published in `r latest_complete_year`, the highest complete publication year in the current corpus, compared with `r fmt(year_n(2010))` in 2010. Records dated `r current_year` are incomplete at the time of analysis and are not interpreted as a complete annual total.

The three largest focal species categories were `r nth_species(1)$species` (`r fmt(nth_species(1)$n)` records; `r pct(nth_species(1)$n)`), `r nth_species(2)$species` (`r fmt(nth_species(2)$n)`; `r pct(nth_species(2)$n)`) and `r nth_species(3)$species` (`r fmt(nth_species(3)$n)`; `r pct(nth_species(3)$n)`). Species categories are not mutually exclusive because individual records can refer to more than one eligible farmed species.

```{r fig-year-species, fig.cap="Records by publication year and focal farmed species."}
include_figure(here::here("visualisations", "figure_01_records_by_publication_year.png"))
```

The thematic composition of the literature also expanded through time. `r topic_name(1, 1)` remained the largest high-level theme in absolute terms, while `r topic_name(1, 2)` and `r topic_name(1, 3)` also increased substantially as the evidence base grew. Because records can receive more than one high-level topic, annual stacked totals represent topic-record assignments rather than mutually exclusive studies.

```{r fig-year-topic, fig.cap="Topic-assignment frequency for high-level topics by publication year."}
include_figure(here::here("visualisations", "figure_05_records_by_publication_year_high_level_topic.png"))
```

## Geography

A substantive study country could be resolved for `r fmt(n_geo_coded)` records (`r pct(n_geo_coded)`), while `r fmt(n_geo_uncoded)` included records (`r pct(n_geo_uncoded)`) did not contain sufficient evidence for a defensible country-level assignment. Among records with assigned geography, the six largest country evidence bases were `r paste(vapply(1:6, function(i) paste0(nth_country(i)$country_name, " (", fmt(nth_country(i)$n), ")"), character(1)), collapse=", ")`. Records may be assigned to more than one country where the substantive study spans multiple countries.

```{r fig-country-species, fig.cap="Records per country for the 20 most frequently represented study countries, by focal farmed species."}
include_figure(here::here("visualisations", "figure_02_records_by_country.png"))
```

```{r fig-choropleth, fig.cap="Global distribution of included records by substantive study country."}
include_figure(here::here("visualisations", "figure_03_choropleth_records_by_country.png"))
```

## Topics

At least one topic was assigned to `r fmt(n_topic_coded)` of the `r fmt(n_total)` included records; `r fmt(n_topic_uncoded)` records (`r pct(n_topic_uncoded)`) remained uncoded for topic. Across coded records, the final ontology contained `r fmt(n_topic_assignments)` distinct record-topic assignments.

The evidence base was strongly oriented towards `r topic_name(1,1)`, represented in `r fmt(topic_count(1,1))` records (`r topic_pct(1,1)`). `r topic_name(1,2)` was the second-largest theme (`r fmt(topic_count(1,2))`; `r topic_pct(1,2)`), followed by `r topic_name(1,3)` (`r fmt(topic_count(1,3))`; `r topic_pct(1,3)`), `r topic_name(1,4)` (`r fmt(topic_count(1,4))`; `r topic_pct(1,4)`) and `r topic_name(1,5)` (`r fmt(topic_count(1,5))`; `r topic_pct(1,5)`). `r topic_name(1,6)` (`r fmt(topic_count(1,6))`; `r topic_pct(1,6)`) and `r topic_name(1,7)` (`r fmt(topic_count(1,7))`; `r topic_pct(1,7)`) were substantially smaller. Theme percentages are not mutually exclusive because a record can be assigned to more than one theme.

```{r fig-top-level-species, fig.cap="High-level topic frequency by focal farmed species. Numbers at bar ends are unique records assigned to each high-level theme; stacked species segments may sum above the unique-record total for multi-species records."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04a_top_level_topics.png"))
```

### Production

Production research was centred on `r human_list(vapply(1:5, function(i) topic_name(2, i, level1="Production"), character(1)))`. The most frequently assigned terminal topic was `r topic_name(3,1,level1="Production")` (`r fmt(topic_count(3,1,level1="Production"))` records; `r topic_pct(3,1,level1="Production")`), followed by `r topic_name(3,2,level1="Production")` (`r fmt(topic_count(3,2,level1="Production"))`; `r topic_pct(3,2,level1="Production")`). Other major concentrations included `r topic_name(3,3,level1="Production")` (`r fmt(topic_count(3,3,level1="Production"))`; `r topic_pct(3,3,level1="Production")`), `r topic_name(3,4,level1="Production")` (`r fmt(topic_count(3,4,level1="Production"))`; `r topic_pct(3,4,level1="Production")`), `r topic_name(3,5,level1="Production")` (`r fmt(topic_count(3,5,level1="Production"))`; `r topic_pct(3,5,level1="Production")`) and `r topic_name(3,6,level1="Production")` (`r fmt(topic_count(3,6,level1="Production"))`; `r topic_pct(3,6,level1="Production")`).

```{r fig-production, fig.cap="Topic-assignment frequency within the Production theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04a_hierarchy_production.png"))
```

### Environment

Environmental research was concentrated in `r topic_name(3,1,level1="Environment")` (`r fmt(topic_count(3,1,level1="Environment"))`; `r topic_pct(3,1,level1="Environment")`), `r topic_name(3,2,level1="Environment")` (`r fmt(topic_count(3,2,level1="Environment"))`; `r topic_pct(3,2,level1="Environment")`), `r topic_name(3,3,level1="Environment")` (`r fmt(topic_count(3,3,level1="Environment"))`; `r topic_pct(3,3,level1="Environment")`) and `r topic_name(3,4,level1="Environment")` (`r fmt(topic_count(3,4,level1="Environment"))`; `r topic_pct(3,4,level1="Environment")`). `r human_list(vapply(5:9, function(i) topic_name(3, i, level1="Environment"), character(1)))` formed a second tier of frequently represented environmental topics.

```{r fig-environment, fig.cap="Topic-assignment frequency within the Environment theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04b_hierarchy_environment.png"))
```

### Methods

Methods research was dominated by `r topic_name(3,1,level1="Methods")` (`r fmt(topic_count(3,1,level1="Methods"))`; `r topic_pct(3,1,level1="Methods")`), followed by `r topic_name(3,2,level1="Methods")` (`r fmt(topic_count(3,2,level1="Methods"))`; `r topic_pct(3,2,level1="Methods")`), `r topic_name(3,3,level1="Methods")` (`r fmt(topic_count(3,3,level1="Methods"))`; `r topic_pct(3,3,level1="Methods")`) and `r topic_name(3,4,level1="Methods")` (`r fmt(topic_count(3,4,level1="Methods"))`; `r topic_pct(3,4,level1="Methods")`).

```{r fig-methods, fig.cap="Topic-assignment frequency within the Methods theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04c_hierarchy_methods.png"))
```

### Industry and governance

Within Industry and governance, `r topic_name(3,1,level1="Industry and governance")` was the largest terminal topic (`r fmt(topic_count(3,1,level1="Industry and governance"))`; `r topic_pct(3,1,level1="Industry and governance")`), followed by `r topic_name(3,2,level1="Industry and governance")` (`r fmt(topic_count(3,2,level1="Industry and governance"))`; `r topic_pct(3,2,level1="Industry and governance")`), `r topic_name(3,3,level1="Industry and governance")` (`r fmt(topic_count(3,3,level1="Industry and governance"))`; `r topic_pct(3,3,level1="Industry and governance")`), `r topic_name(3,4,level1="Industry and governance")` (`r fmt(topic_count(3,4,level1="Industry and governance"))`; `r topic_pct(3,4,level1="Industry and governance")`) and `r topic_name(3,5,level1="Industry and governance")` (`r fmt(topic_count(3,5,level1="Industry and governance"))`; `r topic_pct(3,5,level1="Industry and governance")`).

```{r fig-industry, fig.cap="Topic-assignment frequency within the Industry and governance theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04d_hierarchy_industry_and_governance.png"))
```

### Product

Product research was led by `r topic_name(3,1,level1="Product")` (`r fmt(topic_count(3,1,level1="Product"))`; `r topic_pct(3,1,level1="Product")`), `r topic_name(3,2,level1="Product")` (`r fmt(topic_count(3,2,level1="Product"))`; `r topic_pct(3,2,level1="Product")`) and `r topic_name(3,3,level1="Product")` (`r fmt(topic_count(3,3,level1="Product"))`; `r topic_pct(3,3,level1="Product")`). `r human_list(vapply(4:7, function(i) topic_name(3, i, level1="Product"), character(1)))` were also prominent.

```{r fig-product, fig.cap="Topic-assignment frequency within the Product theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04e_hierarchy_product.png"))
```

### People and society

People and society was much smaller than the Production and Environment evidence bases. The largest terminal topics were `r topic_name(3,1,level1="People and society")` (`r fmt(topic_count(3,1,level1="People and society"))`; `r topic_pct(3,1,level1="People and society")`), `r topic_name(3,2,level1="People and society")` (`r fmt(topic_count(3,2,level1="People and society"))`; `r topic_pct(3,2,level1="People and society")`) and `r topic_name(3,3,level1="People and society")` (`r fmt(topic_count(3,3,level1="People and society"))`; `r topic_pct(3,3,level1="People and society")`). The smallest terminal topic was `r topic_name(3,1,level1="People and society",smallest=TRUE)` (`r fmt(topic_count(3,1,level1="People and society",smallest=TRUE))`; `r topic_pct(3,1,level1="People and society",smallest=TRUE)`).

```{r fig-people, fig.cap="Topic-assignment frequency within the People and society theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04f_hierarchy_people_and_society.png"))
```

### Inputs and resources

Inputs and resources was the smallest high-level theme. `r topic_name(3,1,level1="Inputs and resources")` accounted for `r fmt(topic_count(3,1,level1="Inputs and resources"))` records (`r topic_pct(3,1,level1="Inputs and resources")`) and was substantially more common than `r human_list(vapply(2:4, function(i) topic_name(3, i, level1="Inputs and resources"), character(1)))`. The least represented terminal topic was `r topic_name(3,1,level1="Inputs and resources",smallest=TRUE)` (`r fmt(topic_count(3,1,level1="Inputs and resources",smallest=TRUE))`; `r topic_pct(3,1,level1="Inputs and resources",smallest=TRUE)`).

```{r fig-inputs, fig.cap="Topic-assignment frequency within the Inputs and resources theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04g_hierarchy_inputs_and_resources.png"))
```

## Comparison with secondary research

The supplied manuscript draft compares this evidence map with a recent umbrella review of 37 systematic reviews across salmon aquaculture. Recalculation against the final canonical evidence map confirms the principal imbalance identified in the draft. Sea lice control and treatment occurs in `r fmt(sum(topic_records$record_id[topic_records$level3 == "Sea lice control and treatment"] %>% unique() %>% length()))` mapped records (`r pct(length(unique(topic_records$record_id[topic_records$level3 == "Sea lice control and treatment"])))`), compared with 8 of 37 systematic reviews (21.6%) in the umbrella-review dataset. By contrast, several of the largest areas in the mapped literature have comparatively little systematic-review coverage, including `r topic_name(3,1,level1="Production")` (`r topic_pct(3,1,level1="Production")` of mapped records), `r topic_name(3,2,level1="Production")` (`r topic_pct(3,2,level1="Production")`), and major disease, environmental and methodological topics.

The social evidence base is particularly weakly represented in the systematic-review literature described in the draft. In the final canonical map, `r topic_name(3,1,level1="People and society")` accounts for `r topic_pct(3,1,level1="People and society")` of records, `r topic_name(3,2,level1="People and society")` for `r topic_pct(3,2,level1="People and society")`, and `r topic_name(3,3,level1="People and society")` for `r topic_pct(3,3,level1="People and society")`; the supplied umbrella-review dataset contains one review on antimicrobial resistance/One Health and none in most of the other social categories. Overall, the comparison continues to indicate that the systematic-review evidence covers a narrower subset of the topics represented across the mapped literature, with particularly strong representation of sea lice and limited coverage of several major physiological, environmental, methodological, governance and social research areas.

```{r fig-secondary, fig.cap="Topic-assignment frequency in the supplied umbrella review of 37 systematic reviews across salmon aquaculture."}
secondary_figure <- Sys.getenv("SECONDARY_REVIEW_FIGURE", unset = here::here("docs", "reporting", "workflow_09", "manuscript", "figure_16_umbrella_review.png"))
if (file.exists(secondary_figure)) knitr::include_graphics(secondary_figure) else cat("[Figure 16 retained from supplied manuscript draft]")
```
