---
title: "The status of academic research on salmon farming: a living evidence map"
subtitle: "Results"
output:
  html_document:
    toc: true
    toc_float: true
  word_document:
    toc: false
bibliography: references.bib
link-citations: true
reference-section-title: References
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
figure_dir <- file.path("outputs", "report", "long_form", "figures")
include_figure <- function(filename) {
  path <- file.path(figure_dir, filename)
  if (file.exists(path)) knitr::include_graphics(path) else cat(sprintf("[Figure pending: %s]", filename))
}
```

# Results

## Review process

The original Lens search produced 19,457 potentially relevant bibliographic records, which were screened manually at title and abstract level; 12,074 records were retained for the original corpus. Following expansion to the five-source search architecture and cross-database reconciliation, the current baseline contained 32,292 deduplicated canonical records. Nine records were excluded before relevance screening on publication-status grounds, leaving 32,283 records for automated relevance screening. Of these, 19,407 were retained and 12,876 excluded at Workflow 04. Subsequent topic-stage eligibility checking and structured human adjudication resulted in a further 290 exclusions, leaving **19,117 records in the final included evidence map**.

Database provenance was retained through deduplication, allowing the contribution and overlap of the five bibliographic sources to be compared before and after relevance screening. The source-contribution analysis shows substantial overlap among databases, while each source also contributes records not represented by the others. The paired figure presents all deduplicated canonical records in black and Workflow 04 screening inclusions in olive green, with exact source intersections shown in the accompanying matrix.

```{r fig-source-contribution, fig.cap="Contribution and overlap of bibliographic databases before and after relevance screening. Black bars show all deduplicated canonical records and olive-green bars show Workflow 04 included records. The matrix identifies the database combination defining each exact intersection."}
include_figure("figure_01_database_contribution_upset.png")
```

The complete search, reconciliation, screening, annotation and adjudication process is summarised in the review flow diagram. The flow distinguishes records removed before screening, relevance-screening exclusions, later eligibility exclusions identified during topic quality control, human-review exclusions, and the final set included in the evidence map.

```{r fig-flow, fig.cap="Flow of records through search, reconciliation, relevance screening, annotation and human adjudication."}
include_figure("figure_02_review_flow.png")
```

## Publication year

The volume of academic evidence on salmon farming has increased substantially over time. As in the earlier corpus, the evidence base is dominated by Atlantic salmon, rainbow trout and records referring to farmed salmon without sufficient information for species-level assignment. The final figure will report the temporal pattern from the current 19,117-record canonical evidence map and exclude the incomplete current publication year from trend interpretation.

```{r fig-year-species, fig.cap="Records by publication year and focal farmed species."}
include_figure("figure_03_records_by_publication_year.png")
```

The thematic composition of the literature also changed through time. The earlier analysis showed the largest absolute growth in Production research, while Environment and Methods became increasingly prominent; the final analysis will recalculate these trajectories from the current canonical topic assignments.

```{r fig-year-topic, fig.cap="Topic-assignment frequency for high-level topics by publication year."}
include_figure("figure_04_records_by_publication_year_high_level_topic.png")
```

## Geography

Research is geographically concentrated in the major salmon-producing regions, while rainbow-trout research is distributed across a broader set of countries. The earlier corpus showed particularly large evidence bases in Norway, Chile, Canada, the United Kingdom and the United States, together with substantial rainbow-trout research in countries including Turkey, Iran, Italy and Spain. Final country rankings and counts will be regenerated from the current Workflow 08 geography layer rather than carried forward from the previous manuscript version.

```{r fig-country-species, fig.cap="Records per country for the most frequently represented study countries, by focal farmed species."}
include_figure("figure_05_records_by_country.png")
```

```{r fig-choropleth, fig.cap="Global distribution of records by substantive study country."}
include_figure("figure_06_choropleth_records_by_country.png")
```

## Topics

The evidence base remains strongly oriented towards Production, with Environment forming the second major body of research. Methods, Industry and governance, Product, People and society, and Inputs and resources form progressively smaller parts of the mapped literature. Because the final topic layer contains 53,288 retained topic assignments across the 19,117 included records, all percentages and theme-specific counts below will be regenerated from the final Workflow 08 topic state rather than copied from the earlier 13,389-record manuscript analysis.

```{r fig-top-level-species, fig.cap="High-level topic frequency by focal farmed species."}
include_figure("figure_07_top_level_topics_by_species.png")
```

### Production

Production research in the previous manuscript was concentrated in fish health, fish performance and biology, feed and nutrition, breeding and reproduction, and stress and mortality. The final figure will retain this descriptive structure while recalculating topic frequencies from the final ontology and analytical retention rules.

```{r fig-production, fig.cap="Topic-assignment frequency within the Production theme."}
include_figure("figure_08_hierarchy_production.png")
```

### Environment

Environmental research spans environmental management, impacts on wild populations and ecosystems, waste and emissions, environmental stressors, physical environmental conditions, escapes and broader environmental impacts. The final text will report the dominant and least represented terminal topics directly from the final topic-assignment table.

```{r fig-environment, fig.cap="Topic-assignment frequency within the Environment theme."}
include_figure("figure_09_hierarchy_environment.png")
```

### Methods

Methods research includes diagnostic and laboratory methods, monitoring and sampling, statistical and modelling methods, sensors and imaging, evidence synthesis and classification, and experimental-design methods.

```{r fig-methods, fig.cap="Topic-assignment frequency within the Methods theme."}
include_figure("figure_10_hierarchy_methods.png")
```

### Industry and governance

Industry and governance research covers governance and policy, sector development, economics and performance, markets and value chains, and firms and industry structure.

```{r fig-industry, fig.cap="Topic-assignment frequency within the Industry and governance theme."}
include_figure("figure_11_hierarchy_industry_and_governance.png")
```

### Product

Product research covers composition and quality, contaminants and food safety, consumer responses, processing and preservation, and human nutrition and health.

```{r fig-product, fig.cap="Topic-assignment frequency within the Product theme."}
include_figure("figure_12_hierarchy_product.png")
```

### People and society

People and society research is smaller than the Production and Environment evidence bases and covers public discourse, conflict and social licence, livelihoods, communities, culture and knowledge, public health, equity and rights, labour and employment, and food security and access.

```{r fig-people, fig.cap="Topic-assignment frequency within the People and society theme."}
include_figure("figure_13_hierarchy_people_and_society.png")
```

### Inputs and resources

Inputs and resources research includes circularity, feed-resource supply and farm inputs. The earlier corpus showed a particularly small literature on energy supply and several other upstream resource inputs; these patterns will be recalculated for the final corpus.

```{r fig-inputs, fig.cap="Topic-assignment frequency within the Inputs and resources theme."}
include_figure("figure_14_hierarchy_inputs_and_resources.png")
```

## Rapidly emerging topics

Relative growth is evaluated against the expansion of the evidence base as a whole, using the mean annual number of assignments during 2010–2014 as the baseline index of 100. In the previous analysis, rapidly growing themes included monitoring and sampling methods, automation and precision aquaculture, smoltification and smolt quality, novel feed resources, welfare, climate change, sensors and imaging, statistical and modelling methods, antimicrobial resistance and One Health, energy and life-cycle impacts, by-products and waste as inputs, and plastics and solid waste. The final figure will regenerate both topic trajectories and the database-wide background trajectory from the final corpus.

```{r fig-emerging, fig.cap="Relative growth of rapidly emerging topics compared with growth of the complete evidence base. Each series is indexed to its mean annual frequency during 2010–2014 where a baseline is available."}
include_figure("figure_15_rapidly_emerging_topics.png")
```

## Comparison with secondary research

The earlier manuscript compared the distribution of primary-study topics with a recent umbrella review of 37 systematic reviews of salmon aquaculture. That comparison showed a markedly narrower distribution of secondary research, with particularly strong representation of sea lice and substantially less review coverage of several major physiological, environmental, methodological, governance and social research areas. This comparison should be regenerated against the final primary-study topic distribution before manuscript submission rather than retaining percentages calculated from the previous 13,389-record corpus.

```{r fig-secondary, fig.cap="Comparison of topic representation in the evidence map with topic coverage in the recent umbrella review of systematic reviews."}
include_figure("figure_16_primary_vs_systematic_reviews.png")
```
