---
title: "The status of academic research on salmon farming: a living evidence map"
subtitle: "Results"
output:
  html_document:
    toc: true
    toc_float: true
  word_document:
    toc: false
bibliography: references.bib
link-citations: true
reference-section-title: References
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(dplyr)
library(tidyr)
library(stringr)
library(readr)
library(jsonlite)
library(here)

source(here::here("visualisations", "canonical_figure_data.R"))

# All analytical results in this document are calculated from the authoritative
# Workflow 08 included-only canonical JSONL at render time.
master <- load_figure_master()
n_total <- nrow(master)

fmt <- function(x) format(as.integer(x), big.mark = ",", scientific = FALSE, trim = TRUE)
pct_total <- function(x) sprintf("%.1f%%", 100 * as.numeric(x) / n_total)

include_figure <- function(...) {
  paths <- c(...)
  hit <- paths[file.exists(paths)]
  if (length(hit)) {
    knitr::include_graphics(hit[[1]])
  } else {
    cat(sprintf("[Figure pending: %s]", paste(paths, collapse = " | ")))
  }
}

# Publication year.
year_counts <- master %>%
  filter(!is.na(year)) %>%
  count(year, name = "n")
year_n <- function(y) {
  x <- year_counts$n[match(y, year_counts$year)]
  ifelse(length(x) && !is.na(x), x, 0L)
}

# Species. Records with multiple eligible species contribute once to each
# species category, matching the manuscript figures.
species_counts <- master %>%
  transmute(record_id, species = final_species) %>%
  separate_rows(species, sep = ";") %>%
  mutate(species = str_trim(species)) %>%
  filter(!is.na(species), species != "") %>%
  distinct(record_id, species) %>%
  count(species, name = "n")
species_n <- function(label) {
  x <- species_counts$n[match(label, species_counts$species)]
  ifelse(length(x) && !is.na(x), x, 0L)
}

# Geography. Use the same country gazetteer and ISO3 logic as the manuscript
# geography figures.
gazetteer <- read_csv(
  here::here("config", "global_country_gazetteer_v3.csv"),
  show_col_types = FALSE,
  progress = FALSE
)
country_lookup <- gazetteer %>%
  transmute(
    iso3c = toupper(str_trim(as.character(iso3c))),
    country_name = str_trim(as.character(country_name)),
    match_type = tolower(str_trim(as.character(match_type))),
    priority = suppressWarnings(as.numeric(priority))
  ) %>%
  filter(
    !is.na(iso3c), iso3c != "",
    !is.na(country_name), country_name != "",
    match_type %in% c("country", "country name")
  ) %>%
  arrange(iso3c, desc(priority), country_name) %>%
  distinct(iso3c, .keep_all = TRUE) %>%
  select(iso3c, country_name)

country_counts <- master %>%
  transmute(
    record_id,
    iso3c = toupper(str_trim(as.character(final_primary_country_iso3c)))
  ) %>%
  filter(!is.na(iso3c), iso3c != "") %>%
  separate_rows(iso3c, sep = ";") %>%
  mutate(iso3c = toupper(str_trim(iso3c))) %>%
  filter(iso3c != "", iso3c != "NONE") %>%
  distinct(record_id, iso3c) %>%
  count(iso3c, name = "n", sort = TRUE) %>%
  left_join(country_lookup, by = "iso3c")
country_n <- function(code) {
  x <- country_counts$n[match(code, country_counts$iso3c)]
  ifelse(length(x) && !is.na(x), x, 0L)
}
n_geo_coded <- sum(toupper(str_trim(master$geography_status)) == "RESOLVED")
n_geo_uncoded <- sum(toupper(str_trim(master$geography_status)) == "NONE")

# Topic assignments.
topic_records <- master %>%
  transmute(record_id, raw_paths = as.character(topic_hierarchy_paths)) %>%
  filter(!is.na(raw_paths), str_trim(raw_paths) != "") %>%
  mutate(path = str_split(raw_paths, "\\s*;\\s*")) %>%
  unnest(path) %>%
  mutate(
    path = str_squish(path),
    level1 = str_squish(str_split_fixed(path, "\\s*>\\s*", 2)[, 1])
  ) %>%
  filter(path != "", level1 != "") %>%
  distinct(record_id, path, level1)

topic_n <- function(path_value) {
  n_distinct(topic_records$record_id[topic_records$path == path_value])
}
theme_n <- function(theme) {
  n_distinct(topic_records$record_id[topic_records$level1 == theme])
}
n_topic_coded <- n_distinct(topic_records$record_id)
n_topic_uncoded <- n_total - n_topic_coded
n_topic_assignments <- nrow(topic_records)

# Rapid-emergence analysis, matching visualisations/06_rapidly_emerging_topics.R.
rapid_topics <- tibble::tribble(
  ~topic, ~path,
  "Monitoring and sampling methods", "Methods > Methodological research > Monitoring and sampling methods",
  "Automation and precision aquaculture", "Production > Production systems and technology > Automation and precision aquaculture",
  "Smoltification and smolt quality", "Production > Early life and transfer > Smoltification and smolt quality",
  "Novel feed resources", "Inputs and resources > Feed-resource supply > Novel feed resources",
  "Welfare assessment and risks", "Production > Fish welfare > Welfare assessment",
  "Welfare assessment and risks", "Production > Fish welfare > Welfare risks and consequences",
  "Climate change", "Environment > Environmental stressors > Climate change",
  "Climate change", "Environment > Climate change > Adaptation and mitigation",
  "Sensors, imaging and measurement", "Methods > Methodological research > Sensors, imaging and measurement methods",
  "Statistical and modelling methods", "Methods > Methodological research > Statistical and modelling methods",
  "Antimicrobial resistance and One Health", "People and society > Public health > Antimicrobial resistance and One Health",
  "Energy, greenhouse gases and life-cycle footprint", "Environment > Resource use and footprint > Energy, greenhouse gases and life-cycle footprint",
  "By-products and waste as inputs", "Inputs and resources > Circularity > By-products and waste as inputs",
  "Plastics and solid waste", "Environment > Waste and emissions > Plastics and solid waste"
)

topic_year <- master %>%
  transmute(record_id, publication_year = year, raw_paths = as.character(topic_hierarchy_paths)) %>%
  filter(!is.na(publication_year), !is.na(raw_paths), str_trim(raw_paths) != "") %>%
  mutate(path = str_split(raw_paths, "\\s*;\\s*")) %>%
  unnest(path) %>%
  mutate(path = str_squish(path)) %>%
  filter(path != "") %>%
  distinct(record_id, publication_year, path) %>%
  inner_join(rapid_topics, by = "path") %>%
  distinct(record_id, publication_year, topic) %>%
  count(topic, publication_year, name = "topic_records")

background_year <- master %>%
  filter(!is.na(year)) %>%
  distinct(record_id, year) %>%
  count(year, name = "background_records")

background_baseline <- mean(background_year$background_records[background_year$year >= 2010 & background_year$year <= 2014])
background_recent <- mean(background_year$background_records[background_year$year >= 2021 & background_year$year <= 2025])
background_growth_ratio <- background_recent / background_baseline

rapid_summary <- rapid_topics %>%
  distinct(topic) %>%
  left_join(
    topic_year %>%
      complete(topic, publication_year = 2010:2025, fill = list(topic_records = 0L)) %>%
      group_by(topic) %>%
      summarise(
        baseline = mean(topic_records[publication_year >= 2010 & publication_year <= 2014]),
        recent = mean(topic_records[publication_year >= 2021 & publication_year <= 2025]),
        .groups = "drop"
      ),
    by = "topic"
  ) %>%
  mutate(
    growth_ratio = if_else(baseline > 0, recent / baseline, NA_real_),
    relative_to_background = growth_ratio / background_growth_ratio
  )
rapid_growth <- function(topic) {
  x <- rapid_summary$growth_ratio[match(topic, rapid_summary$topic)]
  ifelse(length(x) && !is.na(x), x, NA_real_)
}

# Flow counts are generated from the pipeline inputs by the Workflow 09 flow
# script. The frozen manifest is only a fallback for a standalone manuscript render.
flow_path <- here::here("visualisations", "figure_07_flow_diagram_counts.json")
if (!file.exists(flow_path)) {
  flow_path <- here::here("docs", "reporting", "workflow_09", "flow_counts.json")
}
flow <- fromJSON(flow_path, simplifyVector = FALSE)$counts
```

# Results

## Review process

Following multi-database retrieval and reconciliation, `r fmt(flow$deduplicated_records)` deduplicated canonical records entered the curation pipeline. Nine records were removed following the retraction/withdrawal sweep. Of the remaining `r fmt(flow$title_abstract_screened)` records, `r fmt(flow$title_abstract_excluded_total)` were excluded during title-and-abstract screening and subsequent eligibility quality control, leaving **`r fmt(n_total)` records in the final included evidence map**. The final canonical total independently reconciles with the Workflow 08 included-only JSONL used for all analyses below.

Database provenance was retained through deduplication, allowing the contribution and overlap of the five bibliographic sources to be compared before and after relevance screening. The paired UpSet-style figure shows the database contribution to the deduplicated corpus and to the set retained at Workflow 04, together with the exact source intersections.

```{r fig-source-contribution, fig.cap="Contribution and overlap of bibliographic databases before and after relevance screening. Black bars show all deduplicated canonical records and blue bars show records retained at Workflow 04; the matrix identifies the database combination defining each exact intersection."}
include_figure(here::here("outputs", "citesource_contribution", "database_contribution_upset.png"))
```

The complete search, reconciliation, repair, screening and annotation process is summarised in the review flow diagram.

```{r fig-flow, fig.cap="Flow of records through database searching, deduplication, record repair and enrichment, retraction screening, title-and-abstract screening, annotation and inclusion in the Living Evidence Map."}
include_figure(here::here("visualisations", "figure_07_flow_diagram.png"))
```

## Publication year

The volume of academic evidence on salmon farming increased markedly over time (Figure 3). There were `r fmt(year_n(2025))` included records published in 2025, the highest complete publication year in the current corpus, compared with `r fmt(year_n(2010))` in 2010. Records dated 2026 are incomplete at the time of analysis and are not interpreted as a complete annual total.

The three largest focal species categories were rainbow trout (`r fmt(species_n("Rainbow trout"))` records; `r pct_total(species_n("Rainbow trout"))`), Atlantic salmon (`r fmt(species_n("Atlantic salmon"))`; `r pct_total(species_n("Atlantic salmon"))`) and unspecified farmed salmon species (`r fmt(species_n("Unspecified species"))`; `r pct_total(species_n("Unspecified species"))`). Species categories are not mutually exclusive because individual records can refer to more than one eligible farmed species.

```{r fig-year-species, fig.cap="Records by publication year and focal farmed species."}
include_figure(here::here("visualisations", "figure_01_records_by_publication_year.png"))
```

The thematic composition of the literature also expanded through time (Figure 4). Production remained the largest high-level theme in absolute terms, while Environment and Methods also increased substantially as the evidence base grew. Because records can receive more than one high-level topic, annual stacked totals represent topic-record assignments rather than mutually exclusive studies.

```{r fig-year-topic, fig.cap="Topic-assignment frequency for high-level topics by publication year."}
include_figure(here::here("visualisations", "figure_05_records_by_publication_year_high_level_topic.png"))
```

## Geography

A substantive study country could be resolved for `r fmt(n_geo_coded)` records (`r pct_total(n_geo_coded)`), while `r fmt(n_geo_uncoded)` included records (`r pct_total(n_geo_uncoded)`) did not contain sufficient evidence for a defensible country-level assignment. Among records with assigned geography, the largest country evidence bases were Norway (`r fmt(country_n("NOR"))` records), Canada (`r fmt(country_n("CAN"))`), Chile (`r fmt(country_n("CHL"))`), the United Kingdom (`r fmt(country_n("GBR"))`), the United States (`r fmt(country_n("USA"))`) and Turkey (`r fmt(country_n("TUR"))`). Records may be assigned to more than one country where the substantive study spans multiple countries.

```{r fig-country-species, fig.cap="Records per country for the 20 most frequently represented study countries, by focal farmed species."}
include_figure(here::here("visualisations", "figure_02_records_by_country.png"))
```

```{r fig-choropleth, fig.cap="Global distribution of included records by substantive study country."}
include_figure(here::here("visualisations", "figure_03_choropleth_records_by_country.png"))
```

## Topics

At least one topic was assigned to `r fmt(n_topic_coded)` of the `r fmt(n_total)` included records; `r fmt(n_topic_uncoded)` records (`r pct_total(n_topic_uncoded)`) remained uncoded for topic. Across coded records, the final ontology contained `r fmt(n_topic_assignments)` distinct record-topic assignments.

The evidence base was strongly oriented towards Production, represented in `r fmt(theme_n("Production"))` records (`r pct_total(theme_n("Production"))`). Environment was the second-largest theme (`r fmt(theme_n("Environment"))`; `r pct_total(theme_n("Environment"))`), followed by Methods (`r fmt(theme_n("Methods"))`; `r pct_total(theme_n("Methods"))`), Product (`r fmt(theme_n("Product"))`; `r pct_total(theme_n("Product"))`) and Industry and governance (`r fmt(theme_n("Industry and governance"))`; `r pct_total(theme_n("Industry and governance"))`). People and society (`r fmt(theme_n("People and society"))`; `r pct_total(theme_n("People and society"))`) and Inputs and resources (`r fmt(theme_n("Inputs and resources"))`; `r pct_total(theme_n("Inputs and resources"))`) were substantially smaller. Theme percentages are not mutually exclusive because a record can be assigned to more than one theme.

```{r fig-top-level-species, fig.cap="High-level topic frequency by focal farmed species. Numbers at bar ends are unique records assigned to each high-level theme; stacked species segments may sum above the unique-record total for multi-species records."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04a_top_level_topics.png"))
```

### Production

Production research was centred on fish performance and biology, fish health, feed and nutrition, breeding and reproduction, and stress and mortality. The most frequently assigned terminal topic was *Physiology, metabolism and biological responses* (`r fmt(topic_n("Production > Fish performance and biology > Physiology, metabolism and biological responses"))` records; `r pct_total(topic_n("Production > Fish performance and biology > Physiology, metabolism and biological responses"))`), followed by *Growth and development* (`r fmt(topic_n("Production > Fish performance and biology > Growth and development"))`; `r pct_total(topic_n("Production > Fish performance and biology > Growth and development"))`). Other major concentrations included *Other diseases - Prevention and treatment* (`r fmt(topic_n("Production > Fish health > Other diseases - Prevention and treatment"))`; `r pct_total(topic_n("Production > Fish health > Other diseases - Prevention and treatment"))`), *Alternative feed ingredients* (`r fmt(topic_n("Production > Feed and nutrition > Alternative feed ingredients"))`; `r pct_total(topic_n("Production > Feed and nutrition > Alternative feed ingredients"))`), *Other diseases - General* (`r fmt(topic_n("Production > Fish health > Other diseases - General"))`; `r pct_total(topic_n("Production > Fish health > Other diseases - General"))`) and *Other diseases - Epidemiology* (`r fmt(topic_n("Production > Fish health > Other diseases - Epidemiology"))`; `r pct_total(topic_n("Production > Fish health > Other diseases - Epidemiology"))`). Sea lice remained a substantial research cluster, including `r fmt(topic_n("Production > Fish health > Sea lice control and treatment"))` records on control and treatment and `r fmt(topic_n("Production > Fish health > Sea lice epidemiology"))` on epidemiology.

```{r fig-production, fig.cap="Topic-assignment frequency within the Production theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04a_hierarchy_production.png"))
```

### Environment

Environmental research was concentrated in *Water and ocean conditions* (`r fmt(topic_n("Environment > Environmental stressors > Water and ocean conditions"))`; `r pct_total(topic_n("Environment > Environmental stressors > Water and ocean conditions"))`), *Nutrients and organic waste* (`r fmt(topic_n("Environment > Waste and emissions > Nutrients and organic waste"))`; `r pct_total(topic_n("Environment > Waste and emissions > Nutrients and organic waste"))`), *Biodiversity and ecosystem effects* (`r fmt(topic_n("Environment > Wild populations and ecosystems > Biodiversity and ecosystem effects"))`; `r pct_total(topic_n("Environment > Wild populations and ecosystems > Biodiversity and ecosystem effects"))`) and *Monitoring and assessment* (`r fmt(topic_n("Environment > Environmental management > Monitoring and assessment"))`; `r pct_total(topic_n("Environment > Environmental management > Monitoring and assessment"))`). Hydrodynamics and water flow, post-escape ecology, chemicals and therapeutants, water quality and sedimentation/benthic impacts formed a second tier of frequently represented environmental topics.

```{r fig-environment, fig.cap="Topic-assignment frequency within the Environment theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04b_hierarchy_environment.png"))
```

### Methods

Methods research was dominated by *Diagnostic and laboratory methods* (`r fmt(topic_n("Methods > Methodological research > Diagnostic and laboratory methods"))`; `r pct_total(topic_n("Methods > Methodological research > Diagnostic and laboratory methods"))`), followed by *Statistical and modelling methods* (`r fmt(topic_n("Methods > Methodological research > Statistical and modelling methods"))`; `r pct_total(topic_n("Methods > Methodological research > Statistical and modelling methods"))`), *Monitoring and sampling methods* (`r fmt(topic_n("Methods > Methodological research > Monitoring and sampling methods"))`; `r pct_total(topic_n("Methods > Methodological research > Monitoring and sampling methods"))`) and *Sensors, imaging and measurement methods* (`r fmt(topic_n("Methods > Methodological research > Sensors, imaging and measurement methods"))`; `r pct_total(topic_n("Methods > Methodological research > Sensors, imaging and measurement methods"))`).

```{r fig-methods, fig.cap="Topic-assignment frequency within the Methods theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04c_hierarchy_methods.png"))
```

### Industry and governance

Within Industry and governance, *Policy and regulation* was the largest terminal topic (`r fmt(topic_n("Industry and governance > Governance and policy > Policy and regulation"))`; `r pct_total(topic_n("Industry and governance > Governance and policy > Policy and regulation"))`), followed by *Costs and profitability* (`r fmt(topic_n("Industry and governance > Economics and performance > Costs and profitability"))`; `r pct_total(topic_n("Industry and governance > Economics and performance > Costs and profitability"))`), *Economic risk, valuation and impact* (`r fmt(topic_n("Industry and governance > Economics and performance > Economic risk, valuation and impact"))`; `r pct_total(topic_n("Industry and governance > Economics and performance > Economic risk, valuation and impact"))`), *History and regional development* (`r fmt(topic_n("Industry and governance > Sector development > History and regional development"))`) and *Supply, demand and prices* (`r fmt(topic_n("Industry and governance > Markets, trade and value chains > Supply, demand and prices"))`).

```{r fig-industry, fig.cap="Topic-assignment frequency within the Industry and governance theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04d_hierarchy_industry_and_governance.png"))
```

### Product

Product research was led by *Nutritional composition* (`r fmt(topic_n("Product > Composition and nutritional value > Nutritional composition"))`; `r pct_total(topic_n("Product > Composition and nutritional value > Nutritional composition"))`), *Physical and visual quality* (`r fmt(topic_n("Product > Fillet and carcass quality > Physical and visual quality"))`; `r pct_total(topic_n("Product > Fillet and carcass quality > Physical and visual quality"))`) and *Contaminants and residues* (`r fmt(topic_n("Product > Composition and nutritional value > Contaminants and residues"))`; `r pct_total(topic_n("Product > Composition and nutritional value > Contaminants and residues"))`). Chemical food safety, sensory properties, yield and body composition, and storage/packaging/shelf life were also prominent.

```{r fig-product, fig.cap="Topic-assignment frequency within the Product theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04e_hierarchy_product.png"))
```

### People and society

People and society was much smaller than the Production and Environment evidence bases. The largest terminal topics were *Antimicrobial resistance and One Health* (`r fmt(topic_n("People and society > Public health > Antimicrobial resistance and One Health"))`; `r pct_total(topic_n("People and society > Public health > Antimicrobial resistance and One Health"))`), *Conflict and social licence* (`r fmt(topic_n("People and society > Communities and livelihoods > Conflict and social licence"))`; `r pct_total(topic_n("People and society > Communities and livelihoods > Conflict and social licence"))`) and *Public discourse and representation* (`r fmt(topic_n("People and society > Culture and knowledge > Public discourse and representation"))`; `r pct_total(topic_n("People and society > Culture and knowledge > Public discourse and representation"))`). Topics relating to livelihoods, Indigenous peoples and rights, employment, food security, working conditions and labour exploitation each represented well under 1% of the full evidence map.

```{r fig-people, fig.cap="Topic-assignment frequency within the People and society theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04f_hierarchy_people_and_society.png"))
```

### Inputs and resources

Inputs and resources was the smallest high-level theme. *By-products and waste as inputs* accounted for `r fmt(topic_n("Inputs and resources > Circularity > By-products and waste as inputs"))` records (`r pct_total(topic_n("Inputs and resources > Circularity > By-products and waste as inputs"))`) and was substantially more common than *Resource efficiency* (`r fmt(topic_n("Inputs and resources > Circularity > Resource efficiency"))`), *Novel feed resources* (`r fmt(topic_n("Inputs and resources > Feed-resource supply > Novel feed resources"))`) and *Marine feed resources* (`r fmt(topic_n("Inputs and resources > Feed-resource supply > Marine feed resources"))`). Energy supply was represented in only `r fmt(topic_n("Inputs and resources > Farm inputs > Energy supply"))` records.

```{r fig-inputs, fig.cap="Topic-assignment frequency within the Inputs and resources theme."}
include_figure(here::here("visualisations", "topic_hierarchy", "figure_04g_hierarchy_inputs_and_resources.png"))
```

## Rapidly emerging topics

The evidence base as a whole grew by `r sprintf("%.2f", background_growth_ratio)` times between the mean annual output in 2010–2014 and 2021–2025. All 11 selected topics with a non-zero 2010–2014 baseline grew faster than this background rate. The strongest relative increases were observed for *Climate change* (`r sprintf("%.1f", rapid_growth("Climate change"))` times its 2010–2014 baseline), *Novel feed resources* (`r sprintf("%.1f", rapid_growth("Novel feed resources"))` times), *Smoltification and smolt quality* (`r sprintf("%.1f", rapid_growth("Smoltification and smolt quality"))` times) and *Automation and precision aquaculture* (`r sprintf("%.1f", rapid_growth("Automation and precision aquaculture"))` times). Monitoring and sampling, sensors and measurement, welfare, antimicrobial resistance and One Health, energy/life-cycle assessment, circular use of by-products, and statistical/modelling methods also grew faster than the database overall. *Plastics and solid waste* had no records during the 2010–2014 baseline period and is therefore shown as an emerging topic without a directly comparable baseline growth ratio.

```{r fig-emerging, fig.cap="Relative growth of rapidly emerging topics compared with growth of the complete evidence base. Topic series are indexed to their mean annual frequency during 2010–2014 where a baseline is available; the dashed grey line represents fitted background database growth."}
include_figure(here::here("visualisations", "figure_06_rapidly_emerging_topics.png"))
```

## Comparison with secondary research

The supplied manuscript draft compares this evidence map with a recent umbrella review of 37 systematic reviews across salmon aquaculture. Recalculation against the final canonical evidence map confirms the principal imbalance identified in the draft. *Sea lice control and treatment* occurs in `r fmt(topic_n("Production > Fish health > Sea lice control and treatment"))` mapped records (`r pct_total(topic_n("Production > Fish health > Sea lice control and treatment"))`), compared with 8 of 37 systematic reviews (21.6%) in the umbrella-review dataset. By contrast, several of the largest areas in the mapped literature have comparatively little systematic-review coverage, including *Physiology, metabolism and biological responses* (`r pct_total(topic_n("Production > Fish performance and biology > Physiology, metabolism and biological responses"))` of mapped records), *Growth and development* (`r pct_total(topic_n("Production > Fish performance and biology > Growth and development"))`), and major disease, environmental and methodological topics.

The social evidence base is particularly weakly represented in the systematic-review literature described in the draft. In the final canonical map, *Antimicrobial resistance and One Health* accounts for `r pct_total(topic_n("People and society > Public health > Antimicrobial resistance and One Health"))` of records, *Conflict and social licence* for `r pct_total(topic_n("People and society > Communities and livelihoods > Conflict and social licence"))`, and *Public discourse and representation* for `r pct_total(topic_n("People and society > Culture and knowledge > Public discourse and representation"))`; the supplied umbrella-review dataset contains one review on antimicrobial resistance/One Health and none in most of the other social categories.

Overall, the comparison continues to indicate that the systematic-review evidence covers a narrower subset of the topics represented across the mapped literature, with particularly strong representation of sea lice and limited coverage of several major physiological, environmental, methodological, governance and social research areas.
